---
title: "Supplemental Material for 'Hidden Lexicase Selection Parameters: Varying Population Size and Test Case Redundancy with Diagnostic Metrics'"
author: "Jose Guadalupe Hernandez, Anil Kumar Saini, Jason H. Moore"
date: "`r Sys.Date()`"
output: bookdown::gitbook
documentclass: book
bibliography: ["packages.bib", "supplemental.bib"]
biblio-style: apalike
nocite: '@*'
link-citations: yes
github-repo: jgh9094/GECCO-2024-LEXIDATE-EVALUATION
description: "Supplemental material"
---

```{r index, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, echo=TRUE}
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)
library(scales) # to access break formatting functions


NAMES = c(50,100,500,1000,5000)
SHAPE <- c(25,21,22,23,24)
cb_palette <- c('#648FFF','#FE6100','#DC267F','#785EF0','#FFB000')
TSIZE <- 16

p_theme <- theme(
  plot.title = element_text( face = "bold", size = 16, hjust=0.5),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  legend.title=element_text(size=16),
  legend.text=element_text(size=16),
  axis.title = element_text(size=16),
  axis.text = element_text(size=16),
  legend.position="bottom",
  panel.background = element_rect(fill = "#f1f2f5",
                                  colour = "white",
                                  size = 0.5, linetype = "solid")
)
```

# Introduction

This is not intended as a stand-alone document, but as a companion to our manuscript.

## About our supplemental material

As you may have noticed (unless you're reading a pdf version of this), our supplemental material is hosted using [GitHub pages](https://pages.github.com/).
We compiled our data analyses and supplemental documentation into this nifty web-accessible book using [bookdown](https://bookdown.org).

The code used for this supplemental material can be found in [this GitHub repository](https://github.com/jgh9094/GPTP-2024-Lexicase-Analysis).

Our supplemental material includes the following:

- Exploitation rate results (Section \@ref(exploitation-rate-results))
- Contradictory rates results w/ 100 standard test cases (Section \@ref(contradictory-objectives-100-results))
- Contradictory rates results w/ 50 redundant test cases (Section \@ref(contradictory-objectives-150-results))
- Contradictory rates results w/ 100 redundant test cases (Section \@ref(contradictory-objectives-200-results))
- Contradictory rates results w/ 200 redundant test cases (Section \@ref(contradictory-objectives-300-results))
- Contradictory rates results w/ 300 redundant test cases (Section \@ref(contradictory-objectives-500-results))

## Contributing authors

- [Jose Guadalupe Hernandez](https://jgh9094.github.io/)
- [Anil Kumar Saini](https://theaksaini.github.io/)
- [Jason H. Moore](https://jasonhmoore.org/)